Model LF

### 2022-09-17 max_dp endogen stød.Rmd

yd_hk_ds_01 = Shock_1$simulation$yd_hk_ds

tilpas_pr_01 = Shock_1$simulation$tilpas_pr

part_01 = Shock_1$simulation$part
```

@@

```{r}
plot(yk_ds_01, col= "red"); lines(yk_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

## Other plots
```{r}
plot(max_dp_03 - max_dp_00, col= "red", ylim= c(0,4));
lines(max_dp_02 - max_dp_00, col="green");
lines(max_dp_01 - max_dp_00, col="black");
legend("top", legend=c("Inflation shock",
                        "participation endo",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red","green", "black"));
grid()
```

>>>>

yd_h1_01 = Shock_1$simulation$yd_h1

w_h_r_01 = Shock_1$simulation$w_h_r

wage_ds_01 = Shock_1$simulation$wage_ds
```

@@

```{r}
plot(wage_ds_01, col= "red"); lines(y_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

## Other plots
```{r}
plot(wage_ds_01 - wage_ds_00, col= "red");
lines(max_dp_02 - max_dp_00, col="green");
lines(max_dp_01 - max_dp_00, col="black");
legend("top", legend=c("Inflation shock",
                        "participation endo",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red","green", "black"));
grid()
```
